% NOTE: This is very inspired by http://www.toofishes.net/blog/latex-resume-follow-up/

\documentclass[10pt,letterpaper]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
%--- Activation of Charter for text and CMR for math
\usepackage[T1]{fontenc}
%--- Font: Pagella
%\usepackage{tgpagella}
%--- Font: Charter
\usepackage{charter}
\usepackage[expert]{mathdesign}
%--- Microtype Package
\usepackage[activate={true,nocompatibility},final,tracking=true,kerning=true,spacing=true,factor=1100,stretch=10,shrink=10]{microtype}
% activate={true,nocompatibility} - activate protrusion and expansion
% final - enable microtype; use "draft" to disable
% tracking=true, kerning=true, spacing=true - activate these techniques
% factor=1100 - add 10% to the protrusion amount (default is 1000)
% stretch=10, shrink=10 - reduce stretchability/shrinkability (default is 20/20)

%\usepackage{sectsty}
%\subsectionfont{\usefont{T1}{qhv}{b}{n}}

\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{indentfirst}
\pagestyle{empty}

\newcommand\textbox[1]{%
  \parbox{.333\textwidth}{#1}%
}

% Make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

\newcommand\linedatRIGHT[1]{
  \par\noindent\rule{17.75cm}{0.4pt}\par\noindent%
  #1\par\noindent%
  \rule[\fontcharht\font`M]{17.75cm}{0.4pt}\par% raise line up by the height of M in the current font
}

\newcommand{\titlePersonalInfo}[6]{
  \begin{center}{\huge \textbf{#1}}
  \\  #2 \ \ \textbullet
    \ \ #3\ \ \textbullet
    \ \ #4\ \ \textbullet
    \ \ #5\ \ \textbullet
    \ \ #6    
  \end{center}
}

\newcommand{\sectionTitle}[1]{
  \hrule
  \vspace{-1.0em} 
  \subsection*{\uppercase{\textbf{#1}}}
  \vspace{-0.3em}
    \hrule
    \vspace{0.5em}  
}

\newcommand{\languageSection}[4]{
  \vspace{-1.0em}
  \begin{center}
    \textbf{Languages - } \textbf{#1}: #2. \textbf{#3}: #4.
  \end{center}
}

\newcommand{\titleExperienceWithoutLocation}[4]{
  \item[]
  {
    \textbox{\textbf{#1}\hfill}\textbox{\hfil \textbf{#2}\hfil}\hfill \textbf{\emph{#3 \textendash \ #4}}
  }
}

\newcommand{\titleExperienceWithLocation}[5]{
  \item[]
  {
    \textbf{#1} \hfill
    \textbf{#2}
  }
  \\{\emph{#3} \hfill \emph{#4 \textendash \ #5}}
}



\begin{document}
    
  \titlePersonalInfo{Gonzalo Martinez Ramirez}{Santiago, Chile}{(+56) 9 9611 2973}{github.com/gmartinezramirez}{gmartinez.cl}{gmartinezramirez@gmail.com}
  
  \sectionTitle{About me}
  
  \noindent I'm seeking a Software Engineering position involving backend systems.
  I give a preference to positions which leverage my background in cluster
  scheduling and container management with \href{aurora.apache.org}{Apache Aurora}
  and \href{mesos.apache.org}{Apache Mesos}.
  
  \noindent I'm passionate about immutable, reliable, automated infrastructure
  that scales with organizational needs.
  \\
  
  \sectionTitle{Work Experience}
  \begin{itemize}[leftmargin=*]
    \parskip=-0.6em
    
    \titleExperienceWithoutLocation{Software Engineer II}{Twitter}{September 2015}{Present}
    \begin{itemize}[label=\textbullet]
      \itemsep0em
      \item Contributed to internal deploy system to allow users to deploy to
      multiple \href{aurora.apache.org}{Apache Aurora} zones.
      \item Independently worked on reducing technical debt on task specific
      observability tooling.
      \item Collaborated with many engineers at Twitter to improve internal
      Python build hygiene.
    \end{itemize}
    
    \titleExperienceWithoutLocation{Twitter}{Software Engineer I}{August 2014}{August 2015}
    \begin{itemize}[label=\textbullet]
      \itemsep0em
      \item Contributed usability fixes to the
      \href{aurora.apache.org}{Apache Aurora} command line client.
      \item Created an analytics pipeline to gain better understanding of
      cluster utilization and allocation.
      \item Worked with operators to increase overall reliability of compute
      cluster.
    \end{itemize}
    
    \titleExperienceWithoutLocation{Twitter}{Intern}{September 2013}{December 2013}
    \begin{itemize}[label=\textbullet]
      \itemsep0em
      \item Improved Aurora preemption to terminate multiple low priority tasks
      in favor of high priority tasks.
      \item Enhanced scheduling algorithm to penalize short lived tasks to
      reduce wasted scheduling attempts.
    \end{itemize}
    
    \titleExperienceWithoutLocation{Twitter}{Intern}{January 2013}{April 2013}
    \begin{itemize}[label=\textbullet]
      \itemsep0em
      \item Designed and implemented a stream filtering system on top of Apache
      Kafka to reduce stream size.
      \item Created a DSL for operators to filter streams of arbitrary Thrift
      messages.
    \end{itemize}
    
    \titleExperienceWithLocation{DISQUS}{San Francisco, CA}{Intern}{May 2012}{August 2012}
    \begin{itemize}[label=\textbullet]
      \itemsep0em
      \item Worked on performance measurement tools to catch regressions before
      systems were deployed.
    \end{itemize}
    
  \end{itemize}
  
  \sectionTitle{Education}  
  \begin{itemize}[leftmargin=*]
    \parskip=-0.5em
    
    \item[]
    {\textbf{University of Santiago} \hfill
      \textbf{Waterloo, ON}
    }
    \\
    {\emph{Bachelor of Software Engineering} \hfill
      \emph{September 2009 - June 2014}}
    
    \begin{itemize}[label=\textbullet]
      \item Related Coursework: Compilers, Programming Languages, Operating
      Systems, Distributed Systems.
      \item Proposed patches to eCryptfs file system to support
      integrity protecting cipher modes for design project.
      \item Created a compiler for a subset of Java 1.3 for the
      x86 architecture for compilers course.
    \end{itemize}
  \end{itemize}
  
  \begin{tabular}{lllc} 
    \textbf{University of Santiago}&Santiago, Chile& & \\
    $\bullet$ \textbf{M.S. in Computer Science (c)}& March 2010 – Expected December 2017. & GPA: 5.2/7.0 & \\
    $\bullet$ \textbf{Computer Science Engineering} & March 2010 – Expected December 2017. & GPA: 5.2/7.0 & \\
    $\bullet$ \textbf{B.S. in Engineering} & March 2010 – Septiembre 2015. & GPA: 5.2/7.0  &\\
  \end{tabular}
  
  \begin{itemize}[label=\textbullet]
    \item Related Coursework: Compilers, Programming Languages, Operating
    Systems, Distributed Systems.
    \item Proposed patches to eCryptfs file system to support
    integrity protecting cipher modes for design project.
    \item Created a compiler for a subset of Java 1.3 for the
    x86 architecture for compilers course.
  \end{itemize}
  
  \sectionTitle{Technical Skills}
  \begin{description}[labelindent=\parindent]
    \parskip=-0.5em
    \item[Languages:] \textbf{Prefer:} Python, Scala \textbf{Have Used:} Java, Ruby, \CPP, JavaScript, \textbf{Want To Use:} Rust
    \item[Systems:] Apache Aurora, Apache Mesos, Docker, Private Cloud
  \end{description}
  
  \languageSection{Spanish}{native}{English}{work level}
  
\end{document}